Beyond conceptual eco-physiological hypotheses: insights from a general size and trait-based model of ectotherm thermal performance

### 2018-02-05 draft.Rnw
landscape table
draft paper!!

\newcommand\T{\rule{0pt}{2.6ex}}

@@

@@

>>>>

\begin{landscape}

@@

\end{landscape}

@@

sco <- tidyr::gather(scenarios,Rate,value,`Max Metabolism`, `Active Metabolism`, `Std Metabolism`)

ggplot(sco) + 
  geom_line(aes(x=Temperature, y=value, linetype=Rate),alpha=0.7) +
  theme_cowplot()+
  facet_grid(Size~Scenario)+
  theme(strip.text = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank())+
  scale_linetype_discrete('')+
  labs(x = expression("Mean temperature " ( degree*C)),
       y=expression(Oxygen~(mg.yr^-1)))

### 2018-02-05 draft_model_only.tex
draft paper!!

\documentclass[a4paper, toc=index,abstract=true]{scrartcl}
\usepackage{gensymb}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{booktabs}
\usepackage{subfig}
\usepackage{placeins}
\usepackage{amsmath}
\usepackage{pdflscape}
\usepackage{multirow}
\usepackage{longtable}
\usepackage[toc,page]{appendix}
\usepackage{array,booktabs}
\usepackage[american]{babel}
\usepackage[backend=biber,
mincitenames = 1,
maxcitenames = 1,
uniquename = false,
uniquelist = false,
citestyle = authoryear-comp]{biblatex}%
\usepackage{lineno, blindtext}
\addbibresource{Sizing-fx-of-temperature.bib}
\captionsetup[table]{singlelinecheck=false}

\title{Beyond conceptual eco-physiological hypotheses: insights from a general size and trait-based model of ectotherm thermal performance}
\author{Philipp Neubauer\\Dragonfly Data Science, Wellington, NZ  \and 
        Ken H. Andersen\\Centre for Ocean Life
        Danish Technical University, Lyngby, Denmark}

\begin{document}

@@

<< setup,echo=FALSE,include=F>>=
knitr::opts_chunk$set(echo = F, message = F,cache=T,autodep = T)

require(dplyr)
require(tidyr)
require(rlang)
require(cowplot)

source('model.R')

@

<<Scenarios>>=

int_m <- 500
int_t <- 500
int_temp <- 50

# Sluggish small
ss <- list(c=0.3,
           beta=0.15,
           delta=4,
           Ea=0.52, 
           gamma=60, 
           h=30, 
           k=1,
           lO=0.5, 
           m=10, 
           n=0.88, 
           O2crit=2, 
           omega=0.25, 
           p=0.8,
           P50=4.2, 
           phi=0.25, 
           q=0.8,
           shape=3,
           temp=seq(5,26,l=int_temp),
           Topt=20, 
           temp_ref=15,
           slope=0,
           tmax=20,
           tr=0.5,
           M=0.1,
           v=6,
           lm=int_m,
           nu=0.8-1,
           dt=int_t,
           min_m=-2,
           max_m= 3
)

# fast small0.8-1
fs <- ss
fs$lO <- 1
fs$k <- 1.5
fs$h <- 60
fs$v <- 1
fs$M <- 1
fs$nu<- 0.8-1
fs$n <- 0.75
fs$p <- 0.8
fs$q <- 0.8
fs$tmax <- 10

fl <- fs
fl$shape <- 0.1
fl$Topt <- 25

sl <- ss
sl$shape <- 0.1
sl$Topt <- 25

scs <- list(ss,fs,sl,fl)
scenarios <- bind_cols(data_frame(Scenario = as.factor(rep(c('M strategy','P strategy','M strategy','P strategy'),each=int_temp)),
                                  O2lim = as.factor(rep(c('Domed','Rising'),each=int_temp*2))),
                       bind_rows(lapply(scs, plot_data_temp)))

scn <- rep(unique(scenarios$Scenario),2)
scz <- rep(unique(scenarios$O2lim),each=2)

@

@@

\begin{figure}
\centering
<<activity, fig.height=7,fig.width=6>>=

sc_act <- gather(scenarios,Activity,value,Optimum, Limit,Realised) %>%
  mutate(Activity = relevel(as.factor(Activity), "Realised"),
         Dispatch = paste(Scenario,O2lim))

cols <- c('#4477AA','#44AA77','#AA7744','#AA4488','#DDDD77')

lab1 <- as_labeller(c(`M strategy Rising` ='c',
                   `M strategy Domed`  ='a',
                   `P strategy Rising` ='g',
                   `P strategy Domed` = 'e'))

lab2 <- as_labeller(c(`M strategy Rising` ='d',
                   `M strategy Domed`  ='b',
                   `P strategy Rising` ='h',
                   `P strategy Domed` = 'f'))

ggsc <- ggplot(sc_act) + 
  geom_line(aes(x=Temperature, y=value, linetype=Activity,col=Activity)) +
  theme_cowplot()+
  scale_color_manual(values = cols, guide='none')+
  scale_linetype(guide='none')+
  facet_wrap(~Dispatch,ncol = 1,labeller = lab1)+
  theme(strip.text = element_text(hjust = 0),
        strip.background = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank()) + 
  labs(x = expression("Mean temperature " ( degree*C)),
       y=expression('Activity ' (tau)))

sco <- tidyr::gather(scenarios,Metabolism,value,Max, Active, Std,Scope) %>%
  mutate(Dispatch = paste(Scenario,O2lim))

ggso <- sco %>%
  ggplot() + 
   geom_line(aes(x=Temperature, y=value, linetype=Metabolism,col=Metabolism)) +
  theme_cowplot()+
  scale_color_manual(values = cols, guide='none')+
  scale_linetype(guide='none')+
  facet_wrap(~Dispatch,ncol = 1,labeller = lab2)+
  theme(strip.text = element_text(hjust = 0),
        strip.background = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank()) + 
  labs(x = expression("Mean temperature " ( degree*C)),
       y=expression(Oxygen~(mg.yr^-1)))

cowplot::plot_grid(ggsc,ggso,ncol=2)

@
\caption{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column [a,c,e]) at increasing temperatures for a 10g fish, with corresponding oxygen demand (right column [b,d,f]); maximum oxygen supply (MOS; green short-dashed), standard metabolism (red long-dashed) and realised (active; blue solid lines) metabolic demand, as well as metabolic scope (orange long-dashed) at activity level $\tau$, for M-strategy (slow life history; a--d) and P-strategy (fast life-history; e--h). For each strategy, the first row (i.e., a--b; e--f) depicts a life-history with a dome-shaped MOS for increasing temperature, and the second row (i.e., c--d; g--h) corresponds to a species with continuously increasing MOS with temperature.}
\label{fig:activity}
\end{figure}

<<size-act,fig.cap='Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column) at increasing temperatures for fish of 5cm (1.25g; a--b); 10cm (10g; c--d) and 20cm (80g; e--f ), for M-strategy (slow life history; left column [a,c,e]) and P-strategy (fast life-history; right column [b,d,f]) species with a dome-shaped maximum metabolic rate with respect to temperature.',fig.align='center'>>=

ssm <- ss
ssm$m <- 1.25

ssl <- ss
ssl$m <- 80

fsm <- fs
fsm$m <- 1.25

fsl <- fs
fsl$m <- 80

scss <- list(ssm,ss,ssl,fsm,fs,fsl)

scenarios_s <- bind_cols(data_frame(Scenario = as.factor(rep(rep(c('M strategy','P strategy'),each=3),each=int_temp)),
                                  Size = as.factor(rep(rep(c('Small','Medium','Large'),2),each=int_temp))),
                       bind_rows(lapply(scss, plot_data_temp)))

sc_acts <- gather(scenarios_s,Activity,value,Optimum, Limit,Realised) %>%
  mutate(Activity = relevel(as.factor(Activity), "Realised"),
         Dispatch = paste(Scenario,Size))

laba <- as_labeller(c(`M strategy Small` ='a',
                   `P strategy Small`  ='b',
                   `M strategy Medium` ='c',
                   `P strategy Medium` = 'd',
                   `M strategy Large` = 'e',
                   `P strategy Large` = 'f'
))

sc_acts$Dispatch <- factor(sc_acts$Dispatch,levels=unique(sc_acts$Dispatch)[order(unlist(laba(unique(sc_acts$Dispatch))))])

ggplot(sc_acts) + 
  geom_line(aes(x=Temperature, y=value, linetype=Activity,col=Activity)) +
  theme_cowplot()+
  scale_color_manual(values = cols, guide='none')+
  scale_linetype(guide='none')+
  facet_wrap(~Dispatch,ncol = 2,labeller = laba)+
  theme(strip.text = element_text(hjust = 0),
        strip.background = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank()) + 
  labs(x = expression("Mean temperature " ( degree*C)),
       y=expression('Activity ' (tau)))

@

@@

<<feeding,fig.cap='Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for a growing fish at 10cm length (10g). Responses are shown for M- and P-strategy (top and bottom rows, respectively), for species with and without oxygen limitation (left and right columns, respectively). Energy and fitness are plotted relative to maximum over all temperatures.',fig.align='center'>>=

lab <- as_labeller(c(`M strategy Rising` ='b',
                   `M strategy Domed`  ='a',
                   `P strategy Rising` ='d',
                   `P strategy Domed` = 'c'))

sc_feed <- scenarios %>%
  #filter(!grepl('large',Scenario)) %>% 
  group_by(Scenario,O2lim) %>%
  mutate(Consumption=sc(Consumption),
         Efficiency=sc(Efficiency),
         Feeding=`Feeding level`,
         `Available Energy` = sc(`C for growth`),
         `Energy` = ifelse(`Available Energy`<0,0,`Available Energy`),
         Fitness = sc(Energy/M)) %>% 
  tidyr::gather(Rate,value,Feeding,Energy,Efficiency,M,Fitness) %>%
  mutate(Rate = factor(Rate,levels = c('Feeding','Energy','Efficiency','M','Fitness')),
         Dispatch = paste(Scenario,O2lim))

ggplot(sc_feed) + 
  geom_line(aes(x=Temperature, y=value, linetype=Rate,col=Rate,group=Rate)) +
  theme_cowplot()+
  facet_wrap(~Dispatch,labeller = lab,ncol=2)+
  theme(strip.text = element_text(hjust = 0),
        strip.background = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank())+
  scale_linetype_manual(values=c(1:4,1),guide='none')+
  scale_color_manual(values = cols,guide='none')+
  labs(x = expression("Mean temperature " ( degree*C)),
       y='Relative rate')

@

@@

<<calc-gouts>>=

gouts <- parallel::mclapply(scs,plot_data_growth_tO2,mc.cores = 2)

@

<<norms, fig.cap='On ecological time-scales, temperature affects size via evolved maturation-reaction norms (\\cite{marty_impact_2011}). Most reaction norms found in nature have a negative slope, meaning for faster growth, maturation occurs at a larger size. Increasing temparture (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (black dots at 50\\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.',fig.align='center'>>=

t_growth <- bind_rows(lapply(1:length(gouts), function(x) {
  y <- gouts[[x]][['t_growth']] 
  y$Scenario <- scn[x]
  y$O2lim <- scz[x]
  y$Dispatch <- paste(scn[x],scz[x])
  y}))

#browser()
norm <- t_growth %>% 
  mutate(Dispatch = paste(Scenario,O2lim)) %>%
  group_by(Dispatch,Temperature) %>%
  summarise(ts=t[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1],
            m=t_length[ifelse(any(abs(allocs-0.5)<0.1),which.min(abs(allocs-0.5)),NA)-1],
            tsq1=t[ifelse(any(abs(allocs-0.75)<0.1),which.min(abs(allocs-0.75)),NA)-1],
            mq1=t_length[ifelse(any(abs(allocs-0.75)<0.1),which.min(abs(allocs-0.75)),NA)-1],
            tsq3=t[ifelse(any(abs(allocs-0.25)<0.1),which.min(abs(allocs-0.25)),NA)-1],
            mq3=t_length[ifelse(any(abs(allocs-0.25)<0.1),which.min(abs(allocs-0.25)),NA)-1])

ggplot() +
  geom_line(aes(x=t, y=t_length,col=Temperature,group=as.factor(Temperature)),data=t_growth) +
  geom_point(aes(x=ts, y=m),data=norm) +
  # geom_point(aes(x=tsq1, y=mq1),data=norm,col=cols[3]) +
  # geom_point(aes(x=tsq3, y=mq3),data=norm,col=cols[3]) +
  #geom_point(data=growth_scenarios[seq.int(1,nrow(growth_scenarios),by = 5),],aes(x=Temperature, y=Temp, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
  theme_cowplot()+
  facet_wrap(~Dispatch,scales='free',ncol=2,labeller = lab)+
  viridis::scale_colour_viridis(expression(Temp~(degree*C)))+
  theme(legend.text = element_text(size=8),
        legend.title = element_text(size=9),
        strip.text = element_text(hjust = 0),
        strip.background = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank())+
  coord_cartesian()+
  labs(y = 'Length (cm)',
       x='Age  (years)')

@

<<size-rates,fig.cap='Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for growing fish of 5cm (1.25g; a--b); 10cm (10g; c--d) and 20cm (80g; e--f ), for M-strategy (slow life history; left column [a,c,e]) and P-strategy (fast life-history; right column [b,d,f]) species with a dome-shaped maximum metabolic rate with respect to temperature.',fig.align='center'>>=

sc_feed <- scenarios_s %>%
  #filter(!grepl('large',Scenario)) %>% 
  group_by(Scenario,Size) %>%
  mutate(Consumption=sc(Consumption),
         Efficiency=sc(Efficiency),
         Feeding=`Feeding level`,
         `Available Energy` = sc(`C for growth`),
         `Energy` = ifelse(`Available Energy`<0,0,`Available Energy`),
         Fitness = sc(Energy/M)) %>% 
  tidyr::gather(Rate,value,Feeding,Energy,Efficiency,M,Fitness) %>%
  mutate(Rate = factor(Rate,levels = c('Feeding','Energy','Efficiency','M','Fitness')),
         Dispatch = paste(Scenario,Size))

sc_feed$Dispatch <- factor(sc_feed$Dispatch,levels=unique(sc_feed$Dispatch)[order(unlist(laba(unique(sc_feed$Dispatch))))])

ggplot(sc_feed) + 
  geom_line(aes(x=Temperature, y=value, linetype=Rate,col=Rate,group=Rate)) +
  theme_cowplot()+
  facet_wrap(~Dispatch,labeller = laba,ncol=2)+
  theme(strip.text = element_text(hjust = 0),
        strip.background = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank())+
  scale_linetype_manual(values=c(1:4,1),guide='none')+
  scale_color_manual(values = cols,guide='none')+
  labs(x = expression("Mean temperature " ( degree*C)),
       y='Relative rate')

@

@@

<<>>=
ssm <- ss
ssm$delta <- 2

ssl <- ss
ssl$delta <- 1

fsm <- fs
fsm$delta <- 2

fsl <- fs
fsl$delta <- 1

scsa <- list(ss,ssm,ssl,fs,fsm,fsl)
scna <- rep(unique(scenarios$Scenario),each=3)
scza <- rep(c('High','Medium','Low'),3)

gouta <- parallel::mclapply(scsa,plot_data_growth_tO2,mc.cores = 3)

@

<<fit, fig.cap='Fitness (R0), relative to maximum fitness within oxygen limited (blue) and non-oxygen limited (teal) P- (dashed lines) and M-strategy (solid lines) species at the assumed maturation-raction norm and base parameters (panel a), and changes in relative fitness with respect to temperature resulting from different levels of activity cost (panel b; blue: $\\delta=4$; orange: $\\delta=2$ and green: $\\delta=1$).',fig.align='center',fig.height=6>>=

R0s <- bind_rows(lapply(1:length(gouts), function(x) {
  y <- data.frame(gouts[[x]]['R0'])
  y$Temperature <-gouts[[x]][['winfs']]$Temperature
  y$Scenario <- scn[x]
  y$O2lim <- scz[x]
  y$Dispatch <- paste(scn[x],scz[x])
  y}))

R0s <- R0s %>% group_by(Scenario) %>%
  mutate(R0 = R0/max(R0, na.rm=T))

f1 <- ggplot(R0s) + 
  geom_line(aes(x=Temperature, y=R0, linetype=Scenario,col=O2lim,group=Dispatch)) +
  theme_cowplot()+
  theme(
        panel.background = element_blank(),
        plot.background = element_blank())+
  scale_linetype_manual(values=c(1:4),guide='none')+
  scale_color_manual(values = cols,guide='none')+
  labs(x = '',
       y=expression('R0/R0'[max])) +
    theme(axis.title.x=element_blank(),
          axis.text.x = element_text(colour = NA))

R0s <- bind_rows(lapply(1:length(gouta), function(x) {
  y <- data.frame(gouta[[x]]['R0'])
  y$Temperature <-gouta[[x]][['winfs']]$Temperature
  y$Scenario <- scna[x]
  y$ActivityCost <- scza[x]
  y$Dispatch <- paste(scna[x],scza[x])
  y}))

R0s <- R0s %>% group_by(Dispatch) %>%
  mutate(R0 = R0/max(R0, na.rm=T))

f2 <- ggplot(R0s) + 
  geom_line(aes(x=Temperature, y=R0, linetype=Scenario,col=ActivityCost,group=Dispatch)) +
  theme_cowplot()+
  theme(
        panel.background = element_blank(),
        plot.background = element_blank())+
  scale_linetype_manual(values=c(1:4),guide='none')+
  scale_color_manual(values = cols,guide='none')+
  labs(x = expression("Mean temperature " ( degree*C)),
       y=expression('R0/R0'[max]))

cowplot::plot_grid(f1,f2,ncol=1,labels = 'auto')

@

@@

<<MRN, fig.cap='Proportion of energy allocated to reproduction, as a function of age (a) and size (b). With a flat maturation-reaction norm, maturation is independent of age, and only size-dependent.',fig.align='center',fig.height=6>>=

lam <- gouts[[1]]$t_growth

mr1 <- ggplot(lam) + 
  geom_line(aes(x=t, y=allocs,col=Temperature,group=as.factor(Temperature))) +
  #geom_point(aes(x=ts, y=m),data=norm) +
  # geom_point(aes(x=tsq1, y=mq1),data=norm,col=cols[3]) +
  # geom_point(aes(x=tsq3, y=mq3),data=norm,col=cols[3]) +
  #geom_point(data=growth_scenarios[seq.int(1,nrow(growth_scenarios),by = 5),],aes(x=Temperature, y=Temp, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
  theme_cowplot()+
  viridis::scale_colour_viridis(expression(Temp~(degree*C)))+
  theme(legend.text = element_text(size=8),
        legend.title = element_text(size=9),
        strip.text = element_text(hjust = 0),
        strip.background = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank())+
  coord_cartesian()+
  labs(y = 'Proportion',
       x='Age  (years)')

mr2 <- ggplot(lam) + 
  geom_line(aes(x=t_length, y=allocs,col=Temperature,group=as.factor(Temperature))) +
  #geom_point(aes(x=ts, y=m),data=norm) +
  # geom_point(aes(x=tsq1, y=mq1),data=norm,col=cols[3]) +
  # geom_point(aes(x=tsq3, y=mq3),data=norm,col=cols[3]) +
  #geom_point(data=growth_scenarios[seq.int(1,nrow(growth_scenarios),by = 5),],aes(x=Temperature, y=Temp, col=Scenario,shape=Scenario),alpha=0.5,size=2) +
  theme_cowplot()+
  viridis::scale_colour_viridis(expression(Temp~(degree*C)))+
  theme(legend.text = element_text(size=8),
        legend.title = element_text(size=9),
        strip.text = element_text(hjust = 0),
        strip.background = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank())+
  coord_cartesian()+
  labs(y = 'Proportion',
       x='Size (cm)')

cowplot::plot_grid(mr1,mr2,ncol=1,labels = 'auto')

@

>>>>

\documentclass[a4paper, toc=index,abstract=true]{scrartcl}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}
\usepackage{gensymb}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{booktabs}
\usepackage{subfig}
\usepackage{placeins}
\usepackage{amsmath}
\usepackage{pdflscape}
\usepackage{multirow}
\usepackage{longtable}
\usepackage[toc,page]{appendix}
\usepackage{array,booktabs}
\usepackage[american]{babel}
\usepackage[backend=biber,
mincitenames = 1,
maxcitenames = 1,
uniquename = false,
uniquelist = false,
citestyle = authoryear-comp]{biblatex}%
\usepackage{lineno, blindtext}
\addbibresource{Sizing-fx-of-temperature.bib}
\captionsetup[table]{singlelinecheck=false}

\title{Beyond conceptual eco-physiological hypotheses: insights from a general size and trait-based model of ectotherm thermal performance}
\author{Philipp Neubauer\\Dragonfly Data Science, Wellington, NZ  \and 
        Ken H. Andersen\\Centre for Ocean Life
        Danish Technical University, Lyngby, Denmark}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

@@

\begin{figure}
\centering

\includegraphics[width=\maxwidth]{images/activity-1}

\caption{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column [a,c,e]) at increasing temperatures for a 10g fish, with corresponding oxygen demand (right column [b,d,f]); maximum oxygen supply (MOS; green short-dashed), standard metabolism (red long-dashed) and realised (active; blue solid lines) metabolic demand, as well as metabolic scope (orange long-dashed) at activity level $\tau$, for M-strategy (slow life history; a--d) and P-strategy (fast life-history; e--h). For each strategy, the first row (i.e., a--b; e--f) depicts a life-history with a dome-shaped MOS for increasing temperature, and the second row (i.e., c--d; g--h) corresponds to a species with continuously increasing MOS with temperature.}
\label{fig:activity}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=\maxwidth]{images/size-act-1}

}

\caption[Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column) at increasing temperatures for fish of 5cm (1.25g]{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column) at increasing temperatures for fish of 5cm (1.25g; a--b); 10cm (10g; c--d) and 20cm (80g; e--f ), for M-strategy (slow life history; left column [a,c,e]) and P-strategy (fast life-history; right column [b,d,f]) species with a dome-shaped maximum metabolic rate with respect to temperature.}\label{fig:size-act}
\end{figure}

@@

\begin{figure}

{\centering \includegraphics[width=\maxwidth]{images/feeding-1}

}

\caption[Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for a growing fish at 10cm length (10g)]{Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for a growing fish at 10cm length (10g). Responses are shown for M- and P-strategy (top and bottom rows, respectively), for species with and without oxygen limitation (left and right columns, respectively). Energy and fitness are plotted relative to maximum over all temperatures.}\label{fig:feeding}
\end{figure}

@@

\begin{figure}

{\centering \includegraphics[width=\maxwidth]{images/norms-1}

}

\caption[On ecological time-scales, temperature affects size via evolved maturation-reaction norms (\cite{marty_impact_2011})]{On ecological time-scales, temperature affects size via evolved maturation-reaction norms (\cite{marty_impact_2011}). Most reaction norms found in nature have a negative slope, meaning for faster growth, maturation occurs at a larger size. Increasing temparture (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth.}\label{fig:norms}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=\maxwidth]{images/size-rates-1}

}

\caption[Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for growing fish of 5cm (1.25g]{Feeding level (blue solid line), available energy $P$ (green long-dashed), efficiency (orange dotted), mortality (red dotted-dashed) and the ratio of $P$ to $M$ (yellow solid) are impacted by changing activity and the metabolic response to temperature for growing fish of 5cm (1.25g; a--b); 10cm (10g; c--d) and 20cm (80g; e--f ), for M-strategy (slow life history; left column [a,c,e]) and P-strategy (fast life-history; right column [b,d,f]) species with a dome-shaped maximum metabolic rate with respect to temperature.}\label{fig:size-rates}
\end{figure}

@@

\begin{figure}

{\centering \includegraphics[width=\maxwidth]{images/fit-1}

}

\caption[Fitness (R0), relative to maximum fitness within oxygen limited (blue) and non-oxygen limited (teal) P- (dashed lines) and M-strategy (solid lines) species at the assumed maturation-raction norm and base parameters (panel a), and changes in relative fitness with respect to temperature resulting from different levels of activity cost (panel b]{Fitness (R0), relative to maximum fitness within oxygen limited (blue) and non-oxygen limited (teal) P- (dashed lines) and M-strategy (solid lines) species at the assumed maturation-raction norm and base parameters (panel a), and changes in relative fitness with respect to temperature resulting from different levels of activity cost (panel b; blue: $\delta=4$; orange: $\delta=2$ and green: $\delta=1$).}\label{fig:fit}
\end{figure}

@@

\begin{figure}

{\centering \includegraphics[width=\maxwidth]{images/MRN-1}

}

\caption[Proportion of energy allocated to reproduction, as a function of age (a) and size (b)]{Proportion of energy allocated to reproduction, as a function of age (a) and size (b). With a flat maturation-reaction norm, maturation is independent of age, and only size-dependent.}\label{fig:MRN}
\end{figure}
